### 2015-11-20 section/3_redundancy.tex
all edits for pldi'16 submission

Informally, we use static analysis to identify a set of 
memory-read instructions that the computation of code $C$
depends on. We refer
to these instructions as \textit{input} instructions for $C$. 
The values returned
from them at run-time will be tracked and compared to identify
redundant computation among different instances of $C$.

Specifically, \Tool first identifies side-effect instructions in $C$,
as 
discussed in Section \ref{sec:s_workless}. 
It then conducts 
backward static slicing 
from these instructions, considering both control and data
dependency. For every memory read instruction $r$ 
(\texttt{read(v)}) that static slicing encounters, \Tool checks whether $r$
satisfies either one of the following two conditions. 
If $r$ does, it is marked as
an \textit{input} instruction; otherwise, \Tool continues growing the
slice beyond $r$.
The two conditions are:
(1) the value of $v$ is defined outside $C$;
(2) $v$ is a heap or global variable.
The rationale for the first condition is that slicing outside $C$ is
unnecessary for redundancy judgement among instances of $C$.
The rationale for the second condition is that tracking data-dependency
through heap or global variables is complicated in multi-threaded C/C++
programs.

@@

First, we avoid tracking multiple read instructions that we can statically 
prove to return the same value.
Since we implement \Tool in LLVM, we leverage the SSA construction and the
\textit{mem2reg} pass in LLVM to avoid unnecessary tracking of
stack variables.
For example, the read of \texttt{max} on line 12 of 
Figure \ref{fig:Apache34464} is an \textit{input} instruction of the 
\texttt{while} loop on the same line. LLVM identifies it as a loop invariant
and lifts the read of \texttt{max}
out of the loop. Consequently, \Tool only records
its value once during each loop, instead of each iteration.
LLVM is conservative in lifting heap/global variables out of
a loop, for fear of changing the location of potential exceptions, etc.
\Tool conducts a best-effort
loop invariant analysis for heap/global variables.
For example, \Tool identifies that the values of
\texttt{aNode->localName} and \texttt{aNode->namespaceURI} do not change
throughout one loop instance
in Figure~\ref{fig:Mozilla477564}, and hence only traces them once
outside the loop. This analysis is sound but not complete.
\Tool may miss some loop invariants. For in-house debugging, since we know
the problem-triggering inputs do not lead to exceptions, this optimization
is safe. For production-run usage, users can turn off this heap/global
variable related optimization.

>>>>

Informally, we use static analysis to identify a set of 
memory-read instructions that the computation of code $C$
depends on. We refer
to these instructions as \textit{input instructions} for $C$. 
The values returned
from them at run-time, referred to as \textit{inputs}, 
will be tracked and compared to identify
redundant computation among different instances of $C$.

Specifically, \Tool first identifies side-effect instructions in $C$,
similar with that in Section \ref{sec:s_workless}. 
It then conducts 
backward static slicing 
from these instructions, considering both control and data
dependency. For every memory read instruction $r$ 
(\texttt{read(v)}) that static slicing encounters, \Tool checks whether $r$
satisfies either one of the following two conditions. 
If $r$ does, it is marked as
an \textit{input} instruction; otherwise, \Tool continues growing the
slice beyond $r$.
The two conditions are:
(1) the value of $v$ is defined outside $C$;
(2) $v$ is a heap or global variable.
The rationale for the first condition is that slicing outside $C$ is
unnecessary for redundancy judgement among instances of $C$.
The rationale for the second condition is that tracking data-dependency
through heap or global variables is complicated in multi-threaded C/C++
programs.

@@

First, we avoid tracking multiple read instructions that we can statically 
prove to return the same value.
Since we implement \Tool in LLVM, we leverage the SSA construction and the
\textit{mem2reg} pass in LLVM to avoid unnecessary tracking of
stack variables.
For example, the read of \texttt{max} on line 10 of 
Figure \ref{fig:Apache34464} is an \textit{input} instruction of the 
\texttt{while} loop on the same line. LLVM identifies it as a loop invariant
and lifts the read of \texttt{max}
out of the loop. Consequently, \Tool only records
its value once during each loop, instead of each iteration.
LLVM is conservative in lifting heap/global variables out of
a loop, for fear of changing the location of potential exceptions, etc.
\Tool conducts a best-effort
loop invariant analysis for heap/global variables.
For example, \Tool identifies that the values of
\texttt{aNode->localName} and \texttt{aNode->namespaceURI} do not change
throughout one loop instance
in Figure~\ref{fig:Mozilla477564}, and hence only traces them once
outside the loop. This analysis is sound but not complete.
\Tool may miss some loop invariants. For in-house debugging, since we know
the problem-triggering inputs do not lead to exceptions, this optimization
is safe. For production-run usage, users can turn off this heap/global
variable related optimization.
